WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-19 paper/ms.tex
remove appendix A.1

An obvious concern that one might have about the WASP-4 timing anomaly
is that there might be a systematic offset between the TESS time
system and the time system in which the previous observations have
been reported.  There is a precedent for this type of error: data from
the Kepler mission was afflicted by a systematic timing error that was
corrected only late in the mission~\citep[][Section
  3.4]{kepler_DR19_2013}. We performed two checks on the calibration of 
the TESS time system, described below.

\subsection{Checking for consistency in the headers of the lightcurve files}
\label{sec:headers}

The TESS lightcurve files provide observation start and end times in
three different time systems: ${\rm JD}_{\rm UTC}$, ${\rm JD}_{\rm
TDB}$, and ${\rm BJD}_{\rm TDB}$.  First, we verified for a few select
lightcurve files that ${\rm JD}_{\rm UTC}$ lagged behind ${\rm
JD}_{\rm TDB}$ by the expected $32.184 + N\,{\rm seconds}$, where $N$
is the number of leap-seconds since 1961. For the relevant observation
time, $N=37$, and the offset was as expected.  Then, using the ${\rm
JD}_{\rm UTC}$ time stamp, we calculated the barycentric correction
using the software written by \citealt{eastman_achieving_2010}.  (For
simplicity, we assumed the TESS spacecraft was located at the Earth's
geocenter, because the light-travel time between the geocenter and the
spacecraft is on the order of only one second.)  This gave us times in
${\rm BJD}_{\rm TDB}$ that agreed with the ${\rm BJD}_{\rm TDB}$ times
that are delivered with the TESS data products.

\subsection{Checking for timing anomalies in other hot Jupiter systems}
\label{sec:hj_verification}

@@

We repeated all the data reduction and analysis steps described in
this paper for other hot Jupiters observed by TESS for which timing
data exists spanning many years.  First, we checked which hot Jupiters
were observed over the first three TESS sectors using a combination of
\texttt{tessmaps}\footnote{\url{github.com/lgbouma/tessmaps}} and
TEPCat \citep{southworth_homogeneous_2011}.  We then selected hot
Jupiters for which there were at least five distinct epochs reported
in the peer-reviewed literature.  We required that each observation be
of a single transit, that the midpoint be fit as a free parameter, and
that the time system be clearly documented.  Our final hot Jupiter
sample included WASP-4b, 5b, 6b, 18b, and 46b.  The collected and
measured times are given in Tables~5, 6, 7, and 8 for each.

>>>>

An obvious concern that one might have about the WASP-4 timing anomaly
is that there might be a systematic offset between the TESS time
system and the time system in which the previous observations have
been reported.  There is a precedent for this type of error: data from
the Kepler mission was afflicted by a systematic timing error that was
corrected only late in the mission~\citep[][Section
  3.4]{kepler_DR19_2013}.

@@

We repeated all the data reduction and analysis steps described in
this paper for other hot Jupiters observed by TESS for which timing
data exists spanning many years.  First, we checked which hot Jupiters
were observed over the first three TESS sectors using a combination of
\texttt{tessmaps}\footnote{\url{github.com/lgbouma/tessmaps}} and
TEPCat \citep{southworth_homogeneous_2011}.  We recalculated the
barycentric corrections using the \citet{eastman_achieving_2010} code,
and found values that agreed with the lightcurve headers to within
about 1 second.  We then selected hot Jupiters for which there were at
least five distinct epochs reported in the peer-reviewed literature.
We required that each observation be of a single transit, that the
midpoint be fit as a free parameter, and that the time system be
clearly documented.  Our final hot Jupiter sample included WASP-4b,
5b, 6b, 18b, and 46b.  The collected and measured times are given in
Tables~5, 6, 7, and 8 for each.
